%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% Website: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{www.linkedin.com/in/dotruong19}{\Large Truong Van Do}} & Email: \href{do.truong1910@icloud.com}{do.truong1910@icloud.com}\\
  \href{https://www.linkedin.com/in/dotruong19/}{www.linkedin.com/in/dotruong19} & Mobile : +(84) 0963 047 046 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    
    \resumeSubheading
      {VNU University of Engineering and Technology}{Ha Noi, Viet Nam}
      {Computer Networks and Data Communication;  GPA: 3.21/4.0}{October. 2020 -- present}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Institute of Military Science and Technology}{17 Hoang Sam Cau giay, Ha Noi}
      {Associate DevOps}{November 2023 - Present}
      \begin{itemize} [noitemsep,topsep=0pt]
    \item Developed and maintained CI/CD pipelines using Gitlab CI/CD, enabling automated building, and
deployment of services.
    \item Fully managed the whole platform, from the infrastructure to the platform services through the CI/CD, / Gitlab CI / ArgoCD/ Helm named template.

\end{itemize}

    \resumeSubheading
      {Viettel High Tech}{40th floor, Landmark Tower Tu Liem, Ha Noi}
      {DevOps intern}{April 2023 - Oct 2023}
      \begin{itemize} [noitemsep,topsep=0pt]
          \item Developed and maintained CI/CD pipelines using Jenkins, enabling automated building, testing, and deployment of applications.
          \item integrated security testing and scanning tool SonarQube to Jenkins pipelines.
          \item Contributed to the development and maintenance of Jenkins's shared library, which serves as a fundamental component used by all pipelines in Jenkins. Collaborated with a team to enhance the library's functionality, ensuring its reliability and usability across various pipeline configurations.
          \item Collected services' logs using Grafana Loki and constructed a Grafana dashboard. Additionally, developed a module to expose the application's metrics to Prometheus.
      \end{itemize}

    \resumeSubheading
      {Institute of Military Science and Technology}{17 Hoang Sam Cau giay, Ha Noi}
      {Web developer intern}{October 2022 - january 2023}
      \resumeItemListStart
        \resumeItem{CDS-OLAI}
          {Developed a graph component using ReactJS to assess the extent of drug exposure and implemented RESTful API integration to calculate the area under the line between two points on the graph.}
        \resumeItem{khoPhuclam-soft}
          {worked with ExpressJS on the back-end to create and maintain RESTful APIs for tracking transactions throughout the day. These APIs facilitate interaction with ReactJS on the front-end.}
      \resumeItemListEnd



  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Helm templates}
      {A helm template project using named template to render manifest files.}
    \resumeSubItem{Todo app}
      {A web application help users organize and manage their tasks.}
    \resumeSubItem{E-commerce web application}
      {A web application written in javascript using ReactJS library and ExpressJS framework.}
%     \resumeSubItem{Mac Setup}
%       {Book that gives step by step instructions on setting up developer environment on Mac OS.}
  \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
\section{Skills}
 \resumeSubHeadingListStart
   \item{
     \textbf{Programming Languages}{: Javascript, C++, SQL, Java}
   }
   \item{
     \textbf{Containerization and Orchestration}{: Kubernetes, Docker}
   }
   \item{
     \textbf{Continuous Integration/Continuous Delivery (CI/CD)}{: Jenkins, GitLab CI/CD, ArgoCD}
   }
   \item{
     \textbf{Monitoring and Alerting}{: Grafana, Prometheus}
   }
 \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
